Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-22 finnormal-nodalida-2015/finnormal2015.tex
stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58516 72bbbca6-d526-0410-a7d9-f06f51895060
smt done, now cbmt
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58517 72bbbca6-d526-0410-a7d9-f06f51895060
smt infos
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58522 72bbbca6-d526-0410-a7d9-f06f51895060
add numbers for unigram cbmt
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58525 72bbbca6-d526-0410-a7d9-f06f51895060
probably want to try unigram and bigram and take the best
git-svn-id: https://svn.code.sf.n

There are a number of areas of research related to the task of text normalisation. Text
proofing tools, such as spelling and grammar checkers CITEXXX can be used to encourage adherence
to particular orthographic or grammatical norms. Accent and diacritic restoration CITEXXX is similar
in that it aims to bring text closer to standard orthography in order to facilitate treatment by 
automatic tools. Another related area is machine translation between different written norms of 
the same language. For example between Norwegian Bokmål and Norwegian Nynorsk CITEXXX.

@@

The corpus was split into three parts, testing, development and training. The testing
and development portions contain 1,000 words each, with the remaining X,000 for training
supervised models.\footnote{The corpus is split into XX files of 500 words each. Files 01--02 
  were used for development; 03--04 for testing and 05--XX for training.}

@@

%Rules: mä -> minä, oon -> olen, ?*nkaa -> ?*n kanssa
%
%Input: Mä oon Inarinkaa
%Step 1: Mä oon Inarinkaa
%        Minä oon Inarinkaa
%Step 2: Mä oon Inarinkaa
%        Minä oon Inarinkaa
%        Mä olen Inarinkaa
%        Minä olen Inarinkaa
%Step 3: Mä oon Inarinkaa
%        Minä oon Inarinkaa
%        Mä olen Inarinkaa
%        Minä olen Inarinkaa
%        Mä oon Inarin kanssa
%        Minä oon Inarin kanssa
%        Mä olen Inarin kanssa
%        Minä olen Inarin kanssa
%Rank:
%	-13.4885 ← minä olen Inarin kanssa
%	-12.7176 ← minä oon Inarin kanssa
%	-12.4408 ← mä olen Inarin kanssa
%	-9.2045 ← mä oon Inarin kanssa
%	-8.8651 ← minä olen Inarinkaa
%	-8.0941 ← minä oon Inarinkaa
%	-7.8174 ← mä olen Inarinkaa
%	-4.5811 ← mä oon Inarinkaa
%Output: Minä olen Inarin kanssa

@@

The target-language model used was the same as in the unsupervised experiments.

@@

\subsubsection{Phrase-based}

@@

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|}
     \hline
    \textbf{System} & \textbf{PER} & \textbf{WER} & \textbf{BLEU} \\
     \hline
     Baseline & 46.12 & 48.04 & 26.31 \\
     \hline
     rules-1 & 38.27 & 41.19 & 32.65 \\
     rules-2 & 38.17 & 35.25 & 36.41 \\
     rules-c & 36.56 & 39.68 & 34.68 \\
     \hline
     CBMT-cn & - & - & - \\
     CBMT-cs & - & - & - \\
     PBMT-cn & - & - & - \\
     PBMT-cs & - & - & - \\
     \hline
  \end{tabular}
  \label{table:results}
  \caption{Results...}
\end{table}

>>>>

There are a number of areas of research related to the task of text normalisation. Text
proofing tools, such as spelling and grammar checkers CITEXXX can be used to encourage adherence
to particular orthographic or grammatical norms. Accent and diacritic restoration CITEXXX is similar
in that it aims to bring text closer to standard orthography in order to facilitate treatment by 
automatic tools. Another related area is machine translation between different written norms of 
the same language. For example between Norwegian Bokmål and Norwegian Nynorsk \cite{unhammer2009}.

@@

The corpus was split into three parts, testing, development and training. The testing
and development portions contain approximately 1,000 words each, with the remaining 2,538 for training
supervised models.\footnote{The corpus is split into XX files of 500 words each. Files 01--02 
  were used for development; 03--04 for testing and 05--XX for training.}

@@

%Rules: mä -> minä, oon -> olen, ?*nkaa -> ?*n kanssa
%
%Input: Mä oon Tomminkaa
%Step 1: Mä oon Tomminkaa
%        Minä oon Tomminkaa
%Step 2: Mä oon Tomminkaa
%        Minä oon Tomminkaa
%        Mä olen Tomminkaa
%        Minä olen Tomminkaa
%Step 3: Mä oon Tomminkaa
%        Minä oon Tomminkaa
%        Mä olen Tomminkaa
%        Minä olen Tomminkaa
%        Mä oon Tommin kanssa
%        Minä oon Tommin kanssa
%        Mä olen Tommin kanssa
%        Minä olen Tommin kanssa
%Rank:
%	-13.4885 ← minä olen Tommin kanssa
%	-12.7176 ← minä oon Tommin kanssa
%	-12.4408 ← mä olen Tommin kanssa
%	-9.2045 ← mä oon Tommin kanssa
%	-8.8651 ← minä olen Tomminkaa
%	-8.0941 ← minä oon Tomminkaa
%	-7.8174 ← mä olen Tomminkaa
%	-4.5811 ← mä oon Tomminkaa
%Output: Minä olen Tommin kanssa

@@

The target-language model corpus used was the same as in the unsupervised experiments.

We trained models based on two approaches, the first being phrase-based machine translation
CITEXXX and the second on character-based machine translation \cite{nakov2012}.

@@

@@

\newcite{nakov2012}

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|}
     \hline
    \textbf{System} & \textbf{PER} & \textbf{WER} & \textbf{BLEU} \\
     \hline
     Baseline & 46.12 & 48.04 & 26.31 \\
     \hline
     rules-1 & 38.27 & 41.19 & 32.65 \\
     rules-2 & 38.17 & 35.25 & 36.41 \\
     rules-c & 36.56 & 39.68 & 34.68 \\
     \hline
     CBMT$^1$-cn & 43.09 & 48.34 & 33.55 \\
     CBMT$^1$-cs & 46.22 & 52.27 & 29.21 \\
     CBMT$^2$-cn & - & - & - \\
     CBMT$^2$-cs & - & - & - \\
     PBMT-cn & 28.05 & 35.42 & 48.37 \\
     PBMT-cs & 27.95 & 36.13 & 46.76 \\
     \hline
  \end{tabular}
  \label{table:results}
  \caption{Results...}
\end{table}
